% =============================================================
% ATS-OPTIMIZED LATEX CODE FOR TDC MATCHMAKER PROJECT
% Add this to your Projects section in your resume
% =============================================================

\textbf{TDC Matchmaker - AI-Powered Matchmaking CRM Platform} $|$ \textit{Next.js 14, Node.js, PostgreSQL, Redis, AWS S3, Gemini AI} \hfill \href{https://github.com/Sarvang18/Matchmaker}{GitHub}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, itemsep=-2pt]\small
\item Architected a full-stack matchmaking CRM system utilizing Next.js 14 App Router and TypeScript, implementing NextAuth.js with JWT-based authentication to secure role-based access for professional matchmakers managing 100+ client profiles.
\item Engineered an AI-powered compatibility engine integrating Google Gemini 2.0 Flash API with custom weighted scoring algorithms across 8 relationship dimensions (age, location, religion, caste, income, education, occupation, family), generating personalized match explanations and ranking top 20 compatible profiles.
\item Built a real-time Kanban pipeline using React DnD (@hello-pangea/dnd) with PostgreSQL and Prisma ORM for relational data persistence, Redis (IORedis) for caching, and AWS S3 integration for scalable profile photo storage and retrieval.
\item Developed an automated email workflow system with magic link authentication using Nodemailer and JWT tokens, enabling secure client response portals with real-time status tracking (Interested/Not Interested) and automated matchmaker notifications.
\end{itemize}

% =============================================================
% ALTERNATIVE SHORTER VERSION (if space is limited)
% =============================================================

\textbf{TDC Matchmaker - AI-Powered CRM Platform} $|$ \textit{Next.js 14, PostgreSQL, Redis, AWS S3, Gemini AI} \hfill \href{https://github.com/Sarvang18/Matchmaker}{GitHub}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, itemsep=-2pt]\small
\item Built a full-stack matchmaking CRM with Next.js 14, implementing NextAuth.js authentication and role-based access control for managing 100+ client profiles with 30+ biodata fields and automated status tracking.
\item Integrated Google Gemini 2.0 Flash API to create an AI compatibility engine with custom weighted scoring across 8 dimensions, ranking top 20 matches with personalized explanations and automated match suggestions.
\item Architected a scalable backend with PostgreSQL, Prisma ORM, Redis caching, and AWS S3 for photo storage, alongside a Kanban board using React DnD for real-time client pipeline management with drag-and-drop functionality.
\item Developed secure magic link email workflows using JWT tokens and Nodemailer, enabling passwordless client portals for match responses with automated status updates and real-time matchmaker notifications.
\end{itemize}

% =============================================================
% TECHNICAL SKILLS ADDITIONS
% Update your Technical Skills section to include:
% =============================================================

% Add to Frontend: shadcn/ui, @hello-pangea/dnd
% Add to Backend: NextAuth.js, Nodemailer, Prisma ORM
% Add to Tools & Libraries: IORedis, date-fns, Zod, Lucide Icons
% Add to AI/ML section (if you have one): Google Gemini 2.0 Flash API

% Example updated Technical Skills section:
%
% \item \textbf{Frontend:} React.js, Next.js 14, Redux Toolkit, Tailwind CSS, shadcn/ui, Framer Motion, Fuse.js
% \item \textbf{Backend:} Node.js, Express.js, NextAuth.js, Socket.io, Nodemailer, Prisma ORM, Server-Sent Events (SSE), Cron Jobs
% \item \textbf{Databases:} MongoDB, PostgreSQL, DynamoDB, Redis (Upstash, IORedis)
% \item \textbf{Tools \& Libraries:} Git, GitHub, Stripe, Razorpay, Multer, Sharp, Zustand, JWT, bcrypt, Zod, date-fns

% =============================================================
% NOTES FOR PLACEMENT IN YOUR RESUME
% =============================================================

% RECOMMENDED PLACEMENT:
% This project should be placed FIRST or SECOND in your Projects section because:
% 1. It's production-level complexity with real business value
% 2. Showcases full-stack + AI integration (currently trending)
% 3. Demonstrates enterprise patterns (authentication, caching, cloud storage)
% 4. More complete than your other projects (has deployment considerations)
%
% SUGGESTED ORDER:
% 1. NicheAI (your current #1 - keep it, very impressive)
% 2. TDC Matchmaker (add this as #2 - shows different skillset)
% 3. Interactive DSA Visualization Platform (keep as #3)
% 4. Remove or condense LMS/Chat App to make room (they're less unique)

% =============================================================
% ATS OPTIMIZATION KEYWORDS INCLUDED
% =============================================================
% 
% These keywords are specifically included for ATS scanning:
% - Next.js 14, TypeScript, Node.js, PostgreSQL, Redis, AWS S3
% - AI/Machine Learning, Gemini AI, API Integration
% - Full-stack, CRM, Authentication, JWT, Role-based access
% - Prisma ORM, Database design, Caching strategies
% - Email automation, Workflow systems, Real-time updates
% - Drag-and-drop, Kanban, Dashboard, Cloud storage
% - Scalable architecture, Security, Magic links
%
% All bullet points follow the CAR format:
% - Context: What you built
% - Action: How you built it (technologies + methods)
% - Result: Impact (scale, performance, user benefit)

